# Th1/Th2 Ratio — 17 h Post-Exercise

```{r}
#| include: false
for (p in c("R/_common.R", "../_common.R", "book/R/_common.R")) if (file.exists(p)) { source(p); break }
```

## Data Import

```{r ratio-17h-data}
fullData <- load_es("book/data/effect_size/Ratio/pre_post17h/Ratio_pre_post17h_r_050.csv")
```

## Primary Meta-Analysis

::: infobox
**Kostrzewa-Nowak et al. (2019)** is removed before pooling and the model re-fitted.
:::

::: panel-tabset
### {meta}
```{r ratio-17h-main-meta}
m6 <- meta::metagen(TE = g, seTE = SE_g, data = fullData, studlab = paste(Study),
                    random = TRUE, method.tau = "HE", fixed = FALSE,
                    hakn = TRUE, prediction = TRUE, sm = "SMD")
print(m6, overall = TRUE)
```

### {metafor}
```{r ratio-17h-main-metafor}
metafor::rma(yi = g, sei = SE_g, data = fullData, slab = paste(Study),
             method = "HE", test = "knha")
```

### Adapted Model {meta}
```{r ratio-17h-main-adapted}
fullData <- drop_kostrzewa19(fullData)
m6 <- meta::metagen(g, seTE = SE_g, data = fullData, studlab = paste(Study),
                    random = TRUE, method.tau = "HE", hakn = TRUE,
                    prediction = TRUE, sm = "SMD", fixed = FALSE)
print(m6, overall = TRUE)
```
:::

## Outlier Detection

```{r ratio-17h-outliers}
outlier <- metaoutliers(y = m6$TE, s2 = m6$seTE^2, model = "RE")
stdres <- outlier$std.res
```

```{r}
#| label: tbl-ratio-17h-resid
#| tbl-cap: "Standardised residuals"
fullData |> select(Short_reference, g) |> mutate(std_res = outlier$std.res) |> nice_table()
```

```{r ratio-17h-outliers-plot}
plot_stdres(stdres)
```

::: {.callout-note}
No outlier.
:::

## Funnel Plot & Influential Cases

```{r ratio-17h-funnel}
#| fig-width: 10
#| fig-height: 8
#| out-width: 100%
funnel_ce(m6)# , ref = 0.6433, xlim = c(-3, 6), ylim = c(2.5, 0))
```

```{r}
#| label: tbl-ratio-17h-dfbetas
#| tbl-cap: "DFBETAS influence diagnostics"
overall_metafor <- rma.mv(g, VE_g, tdist = TRUE, data = fullData)
df_betas <- dfbetas(overall_metafor)
fullData |> select(Short_reference, g) |> mutate(dfbetas = df_betas) |> nice_table()
```

::: {.callout-note}
No influential case.
:::

## Forest Plot

```{r ratio-17h-forest}
#| fig-width: 12
#| fig-height: 8
#| out-width: 100%
forest_main(m6, xlim = c(-2, 5), left = "Lower at post+17h", right = "Higher at post+17h")
```

## Asymmetry Test

```{r ratio-17h-egger}
metabias(m6, method = "linreg")
```

::: {.callout-note}
No asymmetry -> no trim-and-fill
:::

## Moderator Analyses

::: {.panel-tabset}

### Risk of Bias

#### Model
```{r ratio-17h-mod-rob}
m1mod <- update(m6, subgroup = RoB, print.subgroup.name = TRUE, fixed = FALSE)
print(m1mod, overall = FALSE)
```

::: {.callout-note}
Not significant results
:::

#### Forrest Plot
```{r ratio-17h-mod-rob-forest}
#| fig-width: 10
#| fig-height: 8
#| out-width: 100%
forest_sub(m1mod, xlim = c(-2, 5), left = "Lower at post+17h", right = "Higher at post+17h")
```

### Intensity

#### Model
```{r ratio-17h-mod-intensity}
m2mod <- update(m6, subgroup = intensity, print.subgroup.name = TRUE, fixed = FALSE)
print(m2mod, overall = FALSE)
```

::: {.callout-important}
Significant results but 10 vs 1
:::

#### Forrest Plot
```{r ratio-17h-mod-intensity-forest}
#| fig-width: 10
#| fig-height: 8
#| out-width: 100%
forest_sub(m2mod, xlim = c(-2, 5), left = "Lower at post+17h", right = "Higher at post+17h")
```

### Continuous Moderators (Meta-Regression)

::: {.panel-tabset}

#### Age
```{r ratio-17h-mr-age}
m1mr <- metareg(m6, age); summary(m1mr)
```

::: {.callout-note}
Not significant
:::

```{r ratio-17h-mr-age-bubble}
#| fig-width: 10
#| fig-height: 8
#| out-width: 100%
bubble_reg(m1mr, "age", "Age (years)")
```

#### BMI
```{r ratio-17h-mr-bmi}
m2mr <- metareg(m6, bmi); summary(m2mr)
```

::: {.callout-note}
Not significant
:::

#### Duration
```{r ratio-17h-mr-duration}
m3mr <- metareg(m6, duration); summary(m3mr)
```

::: {.callout-note}
Not significant
:::

#### Dose
```{r ratio-17h-mr-dose}
m4mr <- metareg(m6, dose); summary(m4mr)
```

::: {.callout-note}
Not significant
:::

#### MET
```{r ratio-17h-mr-met}
# MET is only modelled when the metabolic-equivalent column is present in the
# effect-size file; the current r = 0.5 export does not include it.
if ("met" %in% names(fullData)) {
  m5mr <- metareg(m6, met); summary(m5mr)      # Not significant
} else {
  message("No 'met' column in this dataset — MET meta-regression skipped.")
}
```

::: {.callout-note}
Only modelled when the MET column is present; the current *r* = 0.5 export does not include it, so this meta-regression is skipped.
:::

#### IFN
```{r ratio-17h-mr-ifn}
m6mr <- metareg(m6, IFN); summary(m6mr)
```

::: {.callout-note}
Not significant
:::

#### IL_4
```{r ratio-17h-mr-il4}
m7mr <- metareg(m6, IL_4); summary(m7mr)
```

::: {.callout-note}
Not significant
:::

#### IL_6
```{r ratio-17h-mr-il6}
m8mr <- metareg(m6, IL_6); summary(m8mr)
```

::: {.callout-important}
Significant
:::

#### IL_10
```{r ratio-17h-mr-il10}
m9mr <- metareg(m6, IL_10); summary(m9mr)
```

::: {.callout-note}
Not significant
:::

#### IL_2
```{r ratio-17h-mr-il2}
m10mr <- metareg(m6, IL_2); summary(m10mr)
```

::: {.callout-note}
Not significant
:::

:::

:::

## Multivariate Models

```{r ratio-17h-multivariate}
rma(yi = g, vi = V_g, mods = ~ intensity * duration, data = fullData,
    slab = paste(Study), method = "HE", test = "knha")
```

::: {.callout-important}
Model significant but no independent predictors
:::
