# T~H~1/T~H~2 ratio - 17 h post-exercise

```{r}
#| include: false
for (p in c("R/_common.R", "../R/_common.R", "book/R/_common.R")) if (file.exists(p)) { source(p); break }
source(file.path(dirname(p), "_chapter_helpers.R"))
knitr::opts_knit$set(root.dir = normalizePath(dirname(dirname(p))))
knitr::opts_chunk$set(echo = FALSE)
cfg <- list(
  id = "ratio-17h",
  outcome = "Ratio",
  win = "pre_post17h",
  M = "m6",
  drop_kost = TRUE,
  tabs = c("M0-meta", "M0-metafor", "M1-meta"),
  forest = list(w = 12, h = 8, args = "xlim = c(-2, 5), left = \"Lower at post+17h\", right = \"Higher at post+17h\""),
  asym = "egger",
  lancaster = FALSE
)
chain <- chapter_chain(cfg)
```

::: {.summary-panel}
[Summary]{.panel-eyebrow}

## Sensitivity Overview

`r badge(reported_id(cfg), MODEL_LABEL[[reported_id(cfg)]], chain[[R_MAIN]][[reported_id(cfg)]]$k)`

```{r}
sens_overview_table(cfg, chain)
```

```{r}
#| fig-height: 2.4
#| out-width: 100%
sens_overview_plot(cfg, chain)
```

## Model Ledger

```{r}
ledger_table(cfg, chain)
```
:::

[Analysis]{.panel-eyebrow .analysis-eyebrow}

```{r}
r_switch(cfg)
```

```{r}
chapter_resources(cfg, chain)
```

## Data Import

```{r}
#| results: asis
sec(sec_data)
```

## Primary Meta-Analysis

::: infobox
**Kostrzewa-Nowak et al. (2019)** is removed before pooling and the model re-fitted.
:::

```{r}
#| results: asis
sec(sec_primary)
```

## Outlier Detection

```{r}
#| results: asis
sec(sec_outlier)
```

::: {.callout-note}
No outlier.
:::

[r = .50]{.callout-r}

::: {.inconsistency}
**Inkonsistenz:** Im R-Skript steht „No outlier“. Bei r = .50 hat Steensberg et al. (2001) einen standardisierten Residualwert von z = -3.10 und liegt damit über der Outlier-Grenze |z| ≥ 3. In Th1 17 h wurde derselbe Fall als Outlier gewertet und ausgeschlossen (M2).
:::

## Funnel Plot & Influential Cases

```{r}
#| results: asis
sec(sec_funnel)
```

::: {.callout-note}
No influential case.
:::

[r = .50]{.callout-r}

## Forest Plot

```{r}
#| results: asis
sec(sec_forest)
```

## Asymmetry Test

```{r}
#| results: asis
sec(sec_asym)
```

::: {.callout-note}
No asymmetry -> no trim-and-fill
:::

[r = .50]{.callout-r}

```{=html}
<div class="r-fixed-start"></div>
```

```{r}
#| include: false
use_main_r()
```

## Moderator Analyses

`r badge(reported_id(cfg), MODEL_LABEL[[reported_id(cfg)]], chain[[R_MAIN]][[reported_id(cfg)]]$k, r = R_MAIN)`

::: {.panel-tabset}

### Risk of Bias

#### Model {.unnumbered}
```{r ratio-17h-mod-rob}
m1mod <- update(m6, subgroup = RoB, print.subgroup.name = TRUE, fixed = FALSE)
report(m1mod, caption = "Subgroup analysis - Risk of Bias")
```

::: {.callout-note}
Not significant results
:::

#### Forest Plot {.unnumbered}

::: panel-tabset
##### Interactive
::: forest-scroll
```{r ratio-17h-mod-rob-forest-plotly}
#| fig-height: 6
#| out-width: 100%
forest_sub_plotly(m1mod, xlim = c(-2, 5), left = "Lower at post+17h", right = "Higher at post+17h")
```
:::

##### RevMan5
```{r ratio-17h-mod-rob-forest}
#| out-width: 100%
forest_sub(m1mod, xlim = c(-2, 5), left = "Lower at post+17h", right = "Higher at post+17h")
```
:::

### Intensity

#### Model {.unnumbered}
```{r ratio-17h-mod-intensity}
m2mod <- update(m6, subgroup = intensity, print.subgroup.name = TRUE, fixed = FALSE)
report(m2mod, caption = "Subgroup analysis - Intensity")
```

::: {.callout-important}
Significant results but 10 vs 1
:::

#### Forest Plot {.unnumbered}

::: panel-tabset
##### Interactive
::: forest-scroll
```{r ratio-17h-mod-intensity-forest-plotly}
#| fig-height: 6
#| out-width: 100%
forest_sub_plotly(m2mod, xlim = c(-2, 5), left = "Lower at post+17h", right = "Higher at post+17h")
```
:::

##### RevMan5
```{r ratio-17h-mod-intensity-forest}
#| out-width: 100%
forest_sub(m2mod, xlim = c(-2, 5), left = "Lower at post+17h", right = "Higher at post+17h")
```
:::

### Continuous Moderators (Meta-Regression)

::: {.panel-tabset}

#### Age {.unnumbered}
```{r ratio-17h-mr-age}
m1mr <- metareg(m6, age); report(m1mr, caption = "Meta-regression - Age")
```

::: {.callout-note}
Not significant
:::

```{r ratio-17h-mr-age-bubble}
#| fig-width: 10
#| fig-height: 8
#| out-width: 100%
bubble_reg(m1mr, "age", "Age (years)")
```

#### BMI {.unnumbered}
```{r ratio-17h-mr-bmi}
m2mr <- metareg(m6, bmi); report(m2mr, caption = "Meta-regression - BMI")
```

::: {.callout-note}
Not significant
:::

#### Duration {.unnumbered}
```{r ratio-17h-mr-duration}
m3mr <- metareg(m6, duration); report(m3mr, caption = "Meta-regression - Duration")
```

::: {.callout-note}
Not significant
:::

#### Dose {.unnumbered}
```{r ratio-17h-mr-dose}
m4mr <- metareg(m6, dose); report(m4mr, caption = "Meta-regression - Dose")
```

::: {.callout-note}
Not significant
:::

#### MET {.unnumbered}
```{r ratio-17h-mr-met}
# MET is only modelled when the metabolic-equivalent column is present in the
# effect-size file; the current r = 0.5 export does not include it.
if ("met" %in% names(fullData)) {
  m5mr <- metareg(m6, met); report(m5mr, caption = "Meta-regression - MET")      # Not significant
} else {
  message("No 'met' column in this dataset - MET meta-regression skipped.")
}
```

::: {.callout-note}
Only modelled when the MET column is present; the current *r* = 0.5 export does not include it, so this meta-regression is skipped.
:::

#### IFN {.unnumbered}
```{r ratio-17h-mr-ifn}
m6mr <- metareg(m6, IFN); report(m6mr, caption = "Meta-regression - IFN")
```

::: {.callout-note}
Not significant
:::

#### IL_4 {.unnumbered}
```{r ratio-17h-mr-il4}
m7mr <- metareg(m6, IL_4); report(m7mr, caption = "Meta-regression - IL_4")
```

::: {.callout-note}
Not significant
:::

#### IL_6 {.unnumbered}
```{r ratio-17h-mr-il6}
m8mr <- metareg(m6, IL_6); report(m8mr, caption = "Meta-regression - IL_6")
```

::: {.callout-important}
Significant
:::

#### IL_10 {.unnumbered}
```{r ratio-17h-mr-il10}
m9mr <- metareg(m6, IL_10); report(m9mr, caption = "Meta-regression - IL_10")
```

::: {.callout-note}
Not significant
:::

#### IL_2 {.unnumbered}
```{r ratio-17h-mr-il2}
m10mr <- metareg(m6, IL_2); report(m10mr, caption = "Meta-regression - IL_2")
```

::: {.callout-note}
Not significant
:::

:::

:::

## Multivariate Models

`r badge(reported_id(cfg), MODEL_LABEL[[reported_id(cfg)]], chain[[R_MAIN]][[reported_id(cfg)]]$k, r = R_MAIN)`

```{r ratio-17h-multivariate}
report(rma(yi = g, vi = V_g, mods = ~ intensity * duration, data = fullData,
    slab = paste(Study), method = "HE", test = "knha"),
       caption = "Multivariate meta-regression")
```

::: {.callout-important}
Model significant but no independent predictors
:::
