# T~H~1/T~H~2 ratio - Immediately post-exercise

```{r}
#| include: false
for (p in c("R/_common.R", "../R/_common.R", "book/R/_common.R")) if (file.exists(p)) { source(p); break }
source(file.path(dirname(p), "_chapter_helpers.R"))
knitr::opts_knit$set(root.dir = normalizePath(dirname(dirname(p))))
knitr::opts_chunk$set(echo = FALSE)
cfg <- list(
  id = "ratio-imm",
  outcome = "Ratio",
  win = "pre_post",
  M = "m5",
  drop_kost = TRUE,
  tabs = c("M0-meta", "M0-metafor", "M1-meta"),
  forest = list(w = 12, h = 8, args = ""),
  asym = "egger",
  lancaster = TRUE
)
chain <- chapter_chain(cfg)
```

::: {.summary-panel}
[Summary]{.panel-eyebrow}

## Sensitivity Overview

`r badge(reported_id(cfg), MODEL_LABEL[[reported_id(cfg)]], chain[[R_MAIN]][[reported_id(cfg)]]$k)`

```{r}
sens_overview_table(cfg, chain)
```

```{r}
#| fig-height: 2.4
#| out-width: 100%
sens_overview_plot(cfg, chain)
```

## Model Ledger

```{r}
ledger_table(cfg, chain)
```
:::

[Analysis]{.panel-eyebrow .analysis-eyebrow}

```{r}
r_switch(cfg)
```

```{r}
chapter_resources(cfg, chain)
```

## Data Import

::: infobox
The base analysis uses the pre-computed Hedges' *g* file for the Th1/Th2 ratio at *r* = 0.5 (`effect_size/Ratio/pre_post/Ratio_pre_post_r_050.csv`). Sensitivity analyses can substitute the *r* = 0.3 / 0.4 / 0.6 / 0.7 files in the same folder. The pipeline column names are mapped to the analysis conventions (`VE_g`, `Sex`, `Age`, `BMI`) by `load_es()`.
:::

```{r}
#| results: asis
sec(sec_data)
```

## Primary Meta-Analysis

::: infobox
`metagen()` fits a random-effects model on the pre-computed effect sizes (*g*, *SE_g*) using the **Hedges-Olkin (HE)** τ² estimator and the **Knapp-Hartung** small-sample correction (`hakn = TRUE`). **Kostrzewa-Nowak et al. (2019)** is removed before pooling and the model re-fitted; `metafor::rma()` cross-validates.
:::

```{r}
#| results: asis
sec(sec_primary)
```

## Outlier Detection

::: infobox
Leave-one-out standardised residuals are computed via `metaoutliers()`, which is passed the **variance** (`m5$seTE^2`). Studies with \|*z*\| \> 3 are flagged as outliers; \|*z*\| \> 1.96 warrants inspection.
:::

```{r}
#| results: asis
sec(sec_outlier)
```

::: {.callout-note}
No outlier.
:::

[r = .50]{.callout-r}

## Funnel Plot & Influential Cases

::: infobox
The contour-enhanced funnel plot shows study estimates against their standard errors; shaded regions mark significance zones (α = 0.10, 0.05, 0.01). The dfbetas diagnostic from `metafor::rma.mv()` identifies **influential cases** - distinct from statistical outliers and not necessarily excluded.
:::

```{r}
#| results: asis
sec(sec_funnel)
```

::: notebox
One value was above 1 and one below −1, so both were identified as influential cases. Neither is an outlier; all outcomes are retained and the sources of heterogeneity are examined in the moderator analysis.
:::

[r = .50]{.callout-r}

## Forest Plot

```{r}
#| results: asis
sec(sec_forest)
```

## Asymmetry Test

::: infobox
Egger's regression test (`method = "linreg"`) evaluates funnel asymmetry as a proxy for small-study/publication effects (one-tailed, *p* \< .10). Where asymmetry is suggested, a trim-and-fill analysis estimates potentially missing studies.
:::

```{r}
#| results: asis
sec(sec_asym)
```

::: {.callout-note}
No asymmetry -> no trim-and-fill
:::

[r = .50]{.callout-r}

## Sensitivity Analyses

```{r}
#| results: asis
sec(sec_lancaster)
```

```{=html}
<div class="r-fixed-start"></div>
```

```{r}
#| include: false
use_main_r()
```

## Moderator Analyses

`r badge(reported_id(cfg), MODEL_LABEL[[reported_id(cfg)]], chain[[R_MAIN]][[reported_id(cfg)]]$k, r = R_MAIN)`

::: {.panel-tabset}

### Risk of Bias

::: infobox
Subgroup analysis by overall RoB rating tests whether study quality moderates the pooled effect; the between-subgroup statistic (*Q_b*) indicates whether subgroup means differ.
:::

#### Model {.unnumbered}
```{r ratio-mod-rob}
m1mod <- update(m5, subgroup = RoB, print.subgroup.name = TRUE, fixed = FALSE)
report(m1mod, caption = "Subgroup analysis - Risk of Bias")
```

::: {.callout-note}
Not significant results
:::

#### Forest Plot {.unnumbered}

::: panel-tabset
##### Interactive
::: forest-scroll
```{r ratio-mod-rob-forest-plotly}
#| fig-height: 6
#| out-width: 100%
forest_sub_plotly(m1mod, xlim = c(-4, 3))
```
:::

##### RevMan5
```{r ratio-mod-rob-forest}
#| out-width: 100%
forest_sub(m1mod, xlim = c(-4, 3))
```
:::

### Sex

#### Model {.unnumbered}
```{r ratio-mod-sex}
m2mod <- update(m5, subgroup = sex, print.subgroup.name = TRUE, fixed = FALSE)
report(m2mod, caption = "Subgroup analysis - Sex")
```

::: {.callout-important}
Significant results but 15 vs 1 vs 2
:::

#### Forest Plot {.unnumbered}

::: panel-tabset
##### Interactive
::: forest-scroll
```{r ratio-mod-sex-forest-plotly}
#| fig-height: 6
#| out-width: 100%
forest_sub_plotly(m2mod, xlim = c(-4, 3))
```
:::

##### RevMan5
```{r ratio-mod-sex-forest}
#| out-width: 100%
forest_sub(m2mod, xlim = c(-4, 3))
```
:::

### Intensity

#### Model {.unnumbered}
```{r ratio-mod-intensity}
fullData_bis <- fullData |> dplyr::filter(!intensity == "")
m1_c <- meta::metagen(g, seTE = SE_g, data = fullData_bis, studlab = paste(Study),
                      random = TRUE, method.tau = "HE", hakn = TRUE,
                      prediction = TRUE, sm = "SMD", fixed = FALSE)
m3mod <- update(m1_c, subgroup = intensity, print.subgroup.name = TRUE, fixed = FALSE)
report(m3mod, caption = "Subgroup analysis - Intensity")
```

::: {.callout-important}
Significant
:::

#### Forest Plot {.unnumbered}

::: panel-tabset
##### Interactive
::: forest-scroll
```{r ratio-mod-intensity-forest-plotly}
#| fig-height: 6
#| out-width: 100%
forest_sub_plotly(m3mod, xlim = c(-4, 3))
```
:::

##### RevMan5
```{r ratio-mod-intensity-forest}
#| out-width: 100%
forest_sub(m3mod, xlim = c(-4, 3))
```
:::

### Staining

```{r ratio-mod-staining}
m_staining <- update(m5, subgroup = staining, print.subgroup.name = TRUE, fixed = FALSE)
report(m_staining, caption = "Subgroup analysis - Staining")
```

::: {.callout-note}
Not significant results
:::

### Continuous Moderators (Meta-Regression)

::: infobox
Continuous moderators are tested via weighted meta-regression (`metareg()`). A significant slope indicates the moderator explains part of the between-study heterogeneity (τ²); bubble plots show the fitted line with 95% CI.
:::

::: {.panel-tabset}

#### Age {.unnumbered}
```{r ratio-mr-age}
m1mr <- metareg(m5, age); report(m1mr, caption = "Meta-regression - Age")
```

::: {.callout-note}
Not significant
:::

```{r ratio-mr-age-bubble}
#| fig-width: 10
#| fig-height: 8
#| out-width: 100%
bubble_reg(m1mr, "age", "Age (years)")
```

#### BMI {.unnumbered}
```{r ratio-mr-bmi}
m2mr <- metareg(m5, bmi); report(m2mr, caption = "Meta-regression - BMI")
```

::: {.callout-note}
Not significant
:::

```{r ratio-mr-bmi-bubble}
#| fig-width: 10
#| fig-height: 8
#| out-width: 100%
bubble_reg(m2mr, "bmi", "BMI (kg/m²)")
```

#### Duration {.unnumbered}
```{r ratio-mr-duration}
m3mr <- metareg(m5, duration); report(m3mr, caption = "Meta-regression - Duration")
```

::: {.callout-important}
Significant
:::

```{r ratio-mr-duration-bubble}
#| fig-width: 10
#| fig-height: 8
#| out-width: 100%
bubble_reg(m3mr, "duration", "Duration (min)")
```

#### Dose {.unnumbered}
```{r ratio-mr-dose}
m4mr <- metareg(m5, dose); report(m4mr, caption = "Meta-regression - Dose")
```

::: {.callout-note}
Not significant
:::

#### IFN {.unnumbered}
```{r ratio-mr-ifn}
m6mr <- metareg(m5, IFN); report(m6mr, caption = "Meta-regression - IFN")
```

::: {.callout-note}
Not significant
:::

#### IL_4 {.unnumbered}
```{r ratio-mr-il4}
m7mr <- metareg(m5, IL_4); report(m7mr, caption = "Meta-regression - IL_4")
```

::: {.callout-note}
Not significant
:::

#### IL_6 {.unnumbered}
```{r ratio-mr-il6}
m8mr <- metareg(m5, IL_6); report(m8mr, caption = "Meta-regression - IL_6")
```

::: {.callout-note}
Not significant
:::

#### IL_10 {.unnumbered}
```{r ratio-mr-il10}
m9mr <- metareg(m5, IL_10); report(m9mr, caption = "Meta-regression - IL_10")
```

::: {.callout-note}
Not significant
:::

#### IL_2 {.unnumbered}
```{r ratio-mr-il2}
m10mr <- metareg(m5, IL_2); report(m10mr, caption = "Meta-regression - IL_2")
```

::: {.callout-note}
Not significant
:::

:::

:::

## Multivariate Models

`r badge(reported_id(cfg), MODEL_LABEL[[reported_id(cfg)]], chain[[R_MAIN]][[reported_id(cfg)]]$k, r = R_MAIN)`

::: infobox
Multivariate meta-regression tests interactions between candidate moderators. None of the models below yields independent predictors.
:::

::: {.panel-tabset}

### Intensity * Duration
```{r ratio-multivariate-int-dur}
report(rma(yi = g, vi = V_g, mods = ~ intensity * duration, data = fullData,
    slab = paste(Study), method = "HE", test = "knha"),
       caption = "Multivariate meta-regression - Intensity * Duration")
```

::: {.callout-note}
Not significant
:::

### IL_10 * IL_4
```{r ratio-multivariate-il10-il4}
report(rma(yi = g, vi = V_g, mods = ~ IL_10 * IL_4, data = fullData,
    slab = paste(Study), method = "HE", test = "knha"),
       caption = "Multivariate meta-regression - IL_10 * IL_4")
```

::: {.callout-note}
Not significant
:::

### IL_2 * IFN
```{r ratio-multivariate-il2-ifn}
report(rma(yi = g, vi = V_g, mods = ~ IL_2 * IFN, data = fullData,
    slab = paste(Study), method = "HE", test = "knha"),
       caption = "Multivariate meta-regression - IL_2 * IFN")
```

::: {.callout-note}
Not significant
:::

:::
