# Th1 — ~2 h Post-Exercise

```{r}
#| include: false
for (p in c("R/_common.R", "../_common.R", "book/R/_common.R")) if (file.exists(p)) { source(p); break }
```

## Data Import

::: infobox
The ~2 h window (`effect_size/Th1/pre_post+2h/Th1_pre_post+2h_r_050.csv`) contains few arms and no cytokine/BMI coverage, so it is reported for the main analysis, outlier check, funnel, forest, and asymmetry only — no moderator modelling is possible. No study is excluded a priori in this window.
:::

```{r th1-2h-data}
fullData <- load_es("book/data/effect_size/Th1/pre_post+2h/Th1_pre_post+2h_r_050.csv")
```

## Primary Meta-Analysis

::: panel-tabset
### {meta}
```{r th1-2h-main-meta}
m1 <- meta::metagen(TE = g, seTE = SE_g, data = fullData, studlab = paste(Study),
                    random = TRUE, method.tau = "HE", fixed = FALSE,
                    hakn = TRUE, prediction = TRUE, sm = "SMD")
print(m1, overall = TRUE)
```

### {metafor}
```{r th1-2h-main-metafor}
metafor::rma(yi = g, sei = SE_g, data = fullData, slab = paste(Study),
             method = "HE", test = "knha")
```
:::

## Outlier Detection

```{r th1-2h-outliers}
outlier <- metaoutliers(y = m1$TE, s2 = m1$seTE^2, model = "RE")
stdres <- outlier$std.res
```

```{r}
#| label: tbl-th1-2h-resid
#| tbl-cap: "Standardised residuals"
fullData |> select(Short_reference, g) |> mutate(std_res = outlier$std.res) |> nice_table()
```

```{r th1-2h-outliers-plot}
plot_stdres(stdres)
```


::: {.callout-note}
No outcome has standardized residuals above 3 or below -3.
:::


## Funnel Plot & Influential Cases

```{r th1-2h-funnel}
#| fig-width: 10
#| fig-height: 8
#| out-width: 100%
funnel_ce(m1)# , ref = 0.99 , xlim = c(-1.5, 4), ylim = c(0.7, 0))

```

```{r}
#| label: tbl-th1-2h-dfbetas
#| tbl-cap: "DFBETAS influence diagnostics"
overall_metafor <- rma.mv(g, VE_g, tdist = TRUE, data = fullData)
df_betas <- dfbetas(overall_metafor)
fullData |> select(Short_reference, g) |> mutate(dfbetas = df_betas) |> nice_table()
```

::: notebox
One value below −1 and one above 1 were identified as influential cases. Neither is an outlier (Kostrzewa-Nowak & Nowak (2020a)a and Tsubakihara et al. (2012)); all outcomes are retained.
:::

## Forest Plot

```{r th1-2h-forest}
#| fig-width: 8
#| fig-height: 4
#| out-width: 100%
forest_main(m1)

## Asymmetry Test

::: warnbox
**Note:** the number of studies (*k* = 5) is too small to reliably test for small-study effects (minimum *k* = 10; Borenstein et al., 2009). No Egger's test or trim-and-fill is performed.
:::
