# Th1 — 17 h Post-Exercise

```{r}
#| include: false
for (p in c("R/_common.R", "../_common.R", "book/R/_common.R")) if (file.exists(p)) { source(p); break }
```

## Data Import

```{r th1-17h-data}
fullData <- load_es("book/data/effect_size/Th1/pre_post17h/Th1_pre_post17h_r_050.csv")
```

## Primary Meta-Analysis

::: infobox
As in the immediate window, **Kostrzewa-Nowak et al. (2019)** is removed before pooling. Outlier detection then flags **Steensberg et al. (2001)**, which is both an outlier and an influential case and is therefore withdrawn from the downstream analyses (`m2_1`).
:::

::: panel-tabset
### {meta}
```{r th1-17h-main_1}
m2 <- meta::metagen(TE = g, seTE = SE_g, data = fullData, studlab = paste(Study),
                    random = TRUE, method.tau = "HE", fixed = FALSE,
                    hakn = TRUE, prediction = TRUE, sm = "SMD")
print(m2, overall = TRUE)
```
### {metafor}
```{r th1-17h-main_2}
metafor::rma(yi = g, sei = SE_g, data = fullData, slab = paste(Study),
             method = "HE", test = "knha")
```

### Adapted Modell {meta}


::: {.callout-caution}
Re-Fit: Removed Konstrezw-Nowak et al. (2019)
:::

```{r th1-17h-main_3}
fullData <- drop_kostrzewa19(fullData)
m2 <- meta::metagen(g, seTE = SE_g, data = fullData, studlab = paste(Study),
                    random = TRUE, method.tau = "HE", hakn = TRUE,
                    prediction = TRUE, sm = "SMD", fixed = FALSE)
print(m2, overall = TRUE)
```
:::

## Outlier Detection

```{r th1-17h-outliers}
outlier <- metaoutliers(y = m2$TE, s2 = m2$seTE^2, model = "RE")
stdres <- outlier$std.res
```

```{r}
#| label: tbl-th1-17h-resid
#| tbl-cap: "Standardised residuals"
fullData |> select(Short_reference, g) |> mutate(std_res = outlier$std.res) |> nice_table()
```

```{r th1-17h-outliers-plot}
plot_stdres(stdres)
```


::: {.callout-note}
One outcome has standardized residuals below -3 (Steensberg et al. (2001)).
:::


## Funnel Plot & Influential Cases

```{r th1-17h-funnel}
#| fig-width: 10
#| fig-height: 8
#| out-width: 100%
funnel_ce(m2)
```

```{r}
#| label: tbl-th1-17h-dfbetas
#| tbl-cap: "DFBETAS influence diagnostics"
overall_metafor <- rma.mv(g, VE_g, tdist = TRUE, data = fullData)
df_betas <- dfbetas(overall_metafor)
fullData |> select(Short_reference, g) |> mutate(dfbetas = df_betas) |> nice_table()
```

::: {.callout-caution}
Steensberg et al. (2001) is < -1 (influential) and also an outlier -> withdrawn.
:::

### Adapted Model
```{r th1-17h-refit}
# Withdraw the outlier/influential case and re-fit
fullData_bis <- fullData |> dplyr::filter(!Study == "Steensberg et al. (2001)")
m2_1 <- meta::metagen(g, seTE = SE_g, data = fullData_bis, studlab = paste(Study),
                      random = TRUE, method.tau = "HE", hakn = TRUE,
                      prediction = TRUE, sm = "SMD", fixed = FALSE)
print(m2_1, overall = TRUE)
```

```{r th1-17h-funnel2}
#| fig-width: 10
#| fig-height: 8
#| out-width: 100%
funnel_ce(m2_1)
```

## Forest Plot

```{r th1-17h-forest}
#| fig-width: 8
#| fig-height: 4
#| out-width: 100%
forest_main(m2_1, xlim = c(-2, 5), left = "Lower at post+17h", right = "Higher at post+17h")
```

## Asymmetry Test

::: {.panel-tabset}

### Egger´s regression test
```{r th1-17h-egger}
metabias(m2_1, method = "linreg")
```

### Trim and Fill
```{r th1-trim_fill}
# Trim-and-fill
res <- metafor::rma(yi = g, vi = V_g, data = fullData_bis, method = "HE")
taf <- metafor::trimfill(res)
print(taf)
```

::: {.callout-note}
# No missing studies
:::

:::
## Moderator Analyses

::: {.panel-tabset}
### Risk of Bias
#### Model
```{r th1-17h-mod-rob}
m1mod <- update(m2_1, subgroup = RoB, print.subgroup.name = TRUE, fixed = FALSE)
print(m1mod, overall = FALSE)
```

::: {.callout-note}
Not significant results
:::

#### Forrest Plot
```{r th1-17h-mod-rob-forest}
#| fig-width: 10
#| fig-height: 8
#| out-width: 100%
forest_sub(m1mod, xlim = c(-2, 5), left = "Lower at post+17h", right = "Higher at post+17h")
```

::: notebox
**Intensity:** all retained arms share the same intensity, so no intensity subgroup analysis is performed.
:::


### Continuous Moderators (Meta-Regression)
::: {.panel-tabset}
#### Age
```{r th1-17h-mr-age}
m1mr <- metareg(m2_1, age); summary(m1mr)
```

::: {.callout-note}
Not significant
:::

```{r th1-17h-mr-age-bubble}
#| fig-width: 10
#| fig-height: 8
#| out-width: 100%
bubble_reg(m1mr, "age", "Age (years)")
```

#### BMI
```{r th1-17h-mr-bmi}
m2mr <- metareg(m2_1, bmi); summary(m2mr)
```

::: {.callout-note}
Not significant results
:::
```{r th1-17h-mr-bmi-bubble}
#| fig-width: 10
#| fig-height: 8
#| out-width: 100%
bubble_reg(m2mr, "bmi", "BMI (kg/m²)")
```

#### Duration
```{r th1-17h-mr-duration}
m3mr <- metareg(m2_1, duration); summary(m3mr)
```
::: {.callout-note}
Not significant results
:::

#### Dose
```{r th1-17h-mr-dose}
m4mr <- metareg(m2_1, dose); summary(m4mr)
```
::: {.callout-note}
Not significant results
:::

#### IFN
```{r th1-17h-mr-ifn}
m6mr <- metareg(m2_1, IFN); summary(m6mr)
```
::: {.callout-note}
Not significant results
:::

#### IL_4
```{r th1-17h-mr-il4}
m7mr <- metareg(m2_1, IL_4); summary(m7mr)
```

::: {.callout-note}
Not significant results
:::

#### IL_6
```{r th1-17h-mr-il6}
m8mr <- metareg(m2_1, IL_6); summary(m8mr)
```

::: {.callout-note}
Not significant results
:::

#### IL_10
```{r th1-17h-mr-il10}
m9mr <- metareg(m2_1, IL_10); summary(m9mr)
```
::: {.callout-note}
Not significant results
:::
#### IL_2
```{r th1-17h-mr-il2}
m10mr <- metareg(m2_1, IL_2); summary(m10mr)
```
::: {.callout-note}
Not significant results
:::

:::
:::

## Multivariate Models

```{r th1-17h-multivariate}
rma(yi = g, vi = V_g, mods = ~ IFN * IL_2, data = fullData_bis,
    slab = paste(Study), method = "HE", test = "knha")
```

::: {.callout-note}
Not significant
:::
