# T~H~1 - 2 h post-exercise

```{r}
#| include: false
for (p in c("R/_common.R", "../R/_common.R", "book/R/_common.R")) if (file.exists(p)) { source(p); break }
source(file.path(dirname(p), "_chapter_helpers.R"))
knitr::opts_knit$set(root.dir = normalizePath(dirname(dirname(p))))
knitr::opts_chunk$set(echo = FALSE)
cfg <- list(
  id = "th1-2h",
  outcome = "Th1",
  win = "pre_post+2h",
  M = "m1",
  drop_kost = FALSE,
  tabs = c("M0-meta", "M0-metafor"),
  forest = list(w = 8, h = 4, args = ""),
  asym = "none",
  lancaster = TRUE
)
chain <- chapter_chain(cfg)
```

::: {.summary-panel}
[Summary]{.panel-eyebrow}

## Sensitivity Overview

`r badge(reported_id(cfg), MODEL_LABEL[[reported_id(cfg)]], chain[[R_MAIN]][[reported_id(cfg)]]$k)`

```{r}
sens_overview_table(cfg, chain)
```

```{r}
#| fig-height: 2.4
#| out-width: 100%
sens_overview_plot(cfg, chain)
```

## Model Ledger

```{r}
ledger_table(cfg, chain)
```
:::

[Analysis]{.panel-eyebrow .analysis-eyebrow}

```{r}
r_switch(cfg)
```

```{r}
chapter_resources(cfg, chain)
```

## Data Import

::: infobox
The ~2 h window (`effect_size/Th1/pre_post+2h/Th1_pre_post+2h_r_050.csv`) contains few arms and no cytokine/BMI coverage, so it is reported for the main analysis, outlier check, funnel, forest, and asymmetry only — no moderator modelling is possible. No study is excluded a priori in this window.
:::

```{r}
#| results: asis
sec(sec_data)
```

## Primary Meta-Analysis

```{r}
#| results: asis
sec(sec_primary)
```

## Outlier Detection

```{r}
#| results: asis
sec(sec_outlier)
```

::: {.callout-note}
No outcome has standardized residuals above 3 or below -3.
:::

[r = .50]{.callout-r}

## Funnel Plot & Influential Cases

```{r}
#| results: asis
sec(sec_funnel)
```

::: notebox
One value below −1 and one above 1 were identified as influential cases. Neither is an outlier (Kostrzewa-Nowak & Nowak (2020a)a and Tsubakihara et al. (2012)); all outcomes are retained.
:::

[r = .50]{.callout-r}

::: {.inconsistency}
**Inkonsistenz:** Die Notiz wurde im R-Skript aus Th1 immediate übernommen. Kostrzewa-Nowak & Nowak (2020a)a und Tsubakihara et al. (2012) sind im +2 h-Datensatz nicht enthalten. Kein DFBETAS-Wert liegt über |1| (größter Betrag: Steensberg et al. (2001), -0.88).
:::

## Forest Plot

```{r}
#| results: asis
sec(sec_forest)
```

## Asymmetry Test

::: warnbox
**Note:** the number of studies (*k* = 5) is too small to reliably test for small-study effects (minimum *k* = 10; Borenstein et al., 2009). No Egger's test or trim-and-fill is performed.
:::

## Sensitivity Analyses

```{r}
#| results: asis
sec(sec_lancaster)
```
