# Th1 — Immediate Post-Exercise

```{r}
#| include: false
for (p in c("R/_common.R", "../_common.R", "book/R/_common.R")) if (file.exists(p)) { source(p); break }
```

## Data Import

::: infobox
The base analysis uses the pre-computed Hedges' *g* file for Th1 at *r* = 0.5 (`effect_size/Th1/pre_post/Th1_pre_post_r_050.csv`). Sensitivity analyses can substitute the *r* = 0.3 / 0.4 / 0.6 / 0.7 files in the same folder. The pipeline column names are mapped to the analysis conventions (`VE_g`, `Sex`, `Age`, `BMI`) by `load_es()`.
:::

```{r th1-data}
fullData <- load_es("book/data/effect_size/Th1/pre_post/Th1_pre_post_r_050.csv")
```

## Primary Meta-Analysis

::: infobox
`metagen()` fits a random-effects model on the pre-computed effect sizes (*g*, *SE_g*) using the **Hedges–Olkin (HE)** τ² estimator and the **Knapp–Hartung** small-sample correction (`hakn = TRUE`). After inspecting the full set,
**Kostrzewa-Nowak et al. (2019)** was detected as very different across meta-analysis and while not influential on the
overall effect, its values were unrealistic and brought substantial misleading variance.
:::

::: panel-tabset
### Full Modell {meta}
```{r th1-main-meta_1}
# Meta-analysis on all arms
m1 <- meta::metagen(TE = g, seTE = SE_g, data = fullData, studlab = paste(Study),
                    random = TRUE, method.tau = "HE", fixed = FALSE,
                    hakn = TRUE, prediction = TRUE, sm = "SMD")
print(m1, overall = TRUE)
```

### Adapted Model {meta}

::: {.callout-caution}
Kostrzewa-Nowak et al. (2019) removed (unrealistic values / misleading variance); re-fit
:::

```{r th1-main-meta_2}
fullData <- drop_kostrzewa19(fullData)
m1 <- meta::metagen(g, seTE = SE_g, data = fullData, studlab = paste(Study),
                    random = TRUE, method.tau = "HE", hakn = TRUE,
                    prediction = TRUE, sm = "SMD", fixed = FALSE)
print(m1, overall = TRUE)
```

### Adapted Model {metafor}

```{r th1-main-metafor}
metafor::rma(yi = g, sei = SE_g, data = fullData, slab = paste(Study),
             method = "HE", test = "knha")
```
:::

## Outlier Detection

::: infobox
Leave-one-out standardised residuals are computed via `metaoutliers()`, which is passed the **variance** (`m1$seTE^2`). Studies with \|*z*\| \> 3 are flagged as outliers; \|*z*\| \> 1.96 warrants inspection.
:::

```{r th1-outliers}
outlier <- metaoutliers(y = m1$TE, s2 = m1$seTE^2, model = "RE")
stdres <- outlier$std.res
```

```{r}
#| label: tbl-th1-imm-resid
#| tbl-cap: "Standardised residuals"
fullData |> select(Short_reference, g) |> mutate(std_res = outlier$std.res) |> nice_table()
```

```{r th1-outliers-plot}
plot_stdres(stdres)
```

::: {.callout-important}
No outcome has standardized residuals above 3 or below -3.
:::



## Funnel Plot & Influential Cases

::: infobox
The contour-enhanced funnel plot shows study estimates against their standard errors; shaded regions mark significance zones (α = 0.10, 0.05, 0.01). The dfbetas diagnostic from `metafor::rma.mv()` identifies **influential cases** — distinct from statistical outliers and not necessarily excluded.
:::

```{r th1-funnel}
#| fig-width: 10
#| fig-height: 8
#| out-width: 100%
funnel_ce(m1)
```

```{r}
#| label: tbl-th1-imm-dfbetas
#| tbl-cap: "DFBETAS influence diagnostics"
overall_metafor <- rma.mv(g, VE_g, tdist = TRUE, data = fullData)
df_betas <- dfbetas(overall_metafor)
fullData |> select(Short_reference, g) |> mutate(dfbetas = df_betas) |> nice_table()
```

::: notebox
One value was below −1 and one above 1, so both were identified as influential cases. However, neither is an outlier (Kostrzewa-Nowak & Nowak (2020a)a and Tsubakihara et al. (2012)). Accordingly, all outcomes are retained, and the sources of heterogeneity are examined in the moderator analysis.
:::

## Forest Plot

```{r th1-forest}
#| fig-width: 8
#| fig-height: 7
#| out-width: 100%
forest_main(m1, xlim = c(-2, 5))
```

## Asymmetry Test

::: infobox
Egger's regression test (`method = "linreg"`) evaluates funnel asymmetry as a proxy for small-study/publication effects (one-tailed, *p* \< .10). Where asymmetry is suggested, a trim-and-fill analysis estimates potentially missing studies.
:::

::: {.panel-tabset}

### Egger´s regression test
```{r th1-egger}
metabias(m1, method = "linreg")
```

### Trim and Fill
```{r th1-trim_fill}
# Trim-and-fill
res <- metafor::rma(yi = g, vi = V_g, data = fullData, method = "HE")
taf <- metafor::trimfill(res)
print(taf)
```

::: {.callout-note}
# No missing studies
:::
:::

## Moderator Analyses

::: {.panel-tabset}

### Risk of Bias

::: infobox
Subgroup analysis by overall RoB rating tests whether study quality moderates the pooled effect; the between-subgroup statistic (*Q_b*) indicates whether subgroup means differ.
:::

#### Model
```{r th1-mod-rob}
m1mod <- update(m1, subgroup = RoB, print.subgroup.name = TRUE, fixed = FALSE)
print(m1mod, overall = FALSE)
```

::: {.callout-note}
Not significant results
:::

#### Forrestplot
```{r th1-mod-rob-forest}
#| fig-width: 10
#| fig-height: 13
#| out-width: 100%
forest_sub(m1mod, xlim = c(-2, 5))
```

### Staining

```{r th1-mod-staining}
m_staining <- update(m1, subgroup = staining, print.subgroup.name = TRUE, fixed = FALSE)
print(m_staining, overall = FALSE)
```

::: {.callout-note}
Not significant results
:::

### Sex

#### Model
```{r th1-mod-sex}
m_sex <- update(m1, subgroup = sex, print.subgroup.name = TRUE, fixed = FALSE)
print(m_sex, overall = FALSE)
```

::: {.callout-important}
Significant results but 14 vs 1 vs 2
:::

#### Forrest Plot
```{r th1-mod-sex-forest}
#| fig-width: 10
#| fig-height: 8
#| out-width: 100%
forest_sub(m_sex, xlim = c(-2, 5))
```

### Intensity
```{r th1-mod-intensity}
# Exclude arms that do not report 'intensity' so they are not counted by default
fullData_bis <- fullData |> dplyr::filter(!intensity == "")
m1_c <- meta::metagen(g, seTE = SE_g, data = fullData_bis, studlab = paste(Study),
                      random = TRUE, method.tau = "HE", hakn = TRUE,
                      prediction = TRUE, sm = "SMD", fixed = FALSE)
m_int <- update(m1_c, subgroup = intensity, print.subgroup.name = TRUE, fixed = FALSE)
print(m_int, overall = FALSE)
```

::: {.callout-important}
Significant results
:::

#### Forrest Plot
```{r th1-mod-intensity-forest}
#| fig-width: 10
#| fig-height: 8
#| out-width: 100%
forest_sub(m_int, xlim = c(-2, 5))
```

### Continuous Moderators (Meta-Regression)

::: infobox
Continuous moderators are tested via weighted meta-regression (`metareg()`). A significant slope indicates the moderator explains part of the between-study heterogeneity (τ²); bubble plots show the fitted line with 95% CI.
:::

::: {.panel-tabset}

#### Age
```{r th1-mr-age}
m1mr <- metareg(m1, age); summary(m1mr)   # Not significant
```
::: {.callout-note}
Not significant
:::

```{r th1-mr-age-bubble}
#| fig-width: 10
#| fig-height: 8
#| out-width: 100%
bubble_reg(m1mr, "age", "Age (years)")
```

#### BMI
```{r th1-mr-bmi}
m2mr <- metareg(m1, bmi); summary(m2mr)
```

::: {.callout-note}
Not significant
:::

```{r th1-mr-bmi-bubble}
#| fig-width: 10
#| fig-height: 8
#| out-width: 100%
bubble_reg(m2mr, "bmi", "BMI (kg/m²)")
```

#### Duration
```{r th1-mr-duration}
m3mr <- metareg(m1, duration); summary(m3mr)
```

::: {.callout-important}
Significant
:::

```{r th1-mr-duration-bubble}
#| fig-width: 10
#| fig-height: 8
#| out-width: 100%
bubble_reg(m3mr, "duration", "Duration (min)")
```

#### Dose
```{r th1-mr-dose}
m4mr <- metareg(m1, dose); summary(m4mr)
```

::: {.callout-important}
Significant — collinear with duration
:::

```{r th1-mr-dose-bubble}
#| fig-width: 10
#| fig-height: 8
#| out-width: 100%
bubble_reg(m4mr, "dose", "Dose")
```

#### IFN
```{r th1-mr-ifn}
m6mr <- metareg(m1, IFN); summary(m6mr)
```

::: {.callout-note}
Not significant
:::

#### IL-4
```{r th1-mr-il4}
m7mr <- metareg(m1, IL_4); summary(m7mr)
```

::: {.callout-note}
Not significant
:::

#### IL-6
```{r th1-mr-il6}
m8mr <- metareg(m1, IL_6); summary(m8mr)
```

::: {.callout-note}
Not significant
:::

#### IL_10
```{r th1-mr-il10}
m9mr <- metareg(m1, IL_10); summary(m9mr)
```

::: {.callout-note}
Not significant
:::

#### IL_2
```{r th1-mr-il2}
m10mr <- metareg(m1, IL_2); summary(m10mr)
```

::: {.callout-note}
Not significant
:::

:::

:::

## Multivariate Models

::: infobox
Multivariate meta-regression tests interactions between candidate moderators. Neither model below yields independent predictors.
:::

::: {.panel-tabset}

### Intensity * Duration
```{r th1-multivariate_1}
rma(yi = g, vi = V_g, mods = ~ intensity * duration, data = fullData,
    slab = paste(Study), method = "HE", test = "knha")
```
::: {.callout-note}
Not significant
:::

### IFN * IL_2
```{r th1-multivariate_2}
rma(yi = g, vi = V_g, mods = ~ IFN * IL_2, data = fullData,
    slab = paste(Study), method = "HE", test = "knha")
```

::: {.callout-note}
Not significant
:::

:::

## Interaction Surface (IFN-γ × IL-2)

```{r th1-heatmap}
#| fig-width: 9
#| fig-height: 7
#| out-width: 90%
# Clean data (finite values only)
fullData_clean <- fullData |>
  dplyr::filter(is.finite(IFN), is.finite(IL_2), is.finite(g), is.finite(V_g))

model <- metafor::rma(yi = g, vi = V_g, mods = ~ IFN * IL_2,
                      data = fullData_clean, method = "HE", test = "knha")

grid <- expand.grid(
  IFN  = seq(min(fullData_clean$IFN), max(fullData_clean$IFN), length.out = 50),
  IL_2 = seq(min(fullData_clean$IL_2), max(fullData_clean$IL_2), length.out = 50)
)
X <- model.matrix(~ IFN * IL_2, data = grid)
grid$pred <- predict(model, newmods = X[, -1])$pred

ggplot(grid, aes(x = IFN, y = IL_2, fill = pred)) +
  geom_tile() +
  scale_fill_viridis_c() +
  labs(x = "IFN-γ", y = "IL-2", fill = "Hedges' g")
```
