# Th2 — Immediate Post-Exercise

```{r}
#| include: false
for (p in c("R/_common.R", "../_common.R", "book/R/_common.R")) if (file.exists(p)) { source(p); break }
```

## Data Import

::: infobox
The base analysis uses the pre-computed Hedges' *g* file for Th2 at *r* = 0.5 (`effect_size/Th2/pre_post/Th2_pre_post_r_050.csv`). Sensitivity analyses can substitute the *r* = 0.3 / 0.4 / 0.6 / 0.7 files in the same folder. The pipeline column names are mapped to the analysis conventions (`VE_g`, `Sex`, `Age`, `BMI`) by `load_es()`.
:::

```{r th2-data}
fullData <- load_es("book/data/effect_size/Th2/pre_post/Th2_pre_post_r_050.csv")
```

## Primary Meta-Analysis

::: infobox
`metagen()` fits a random-effects model on the pre-computed effect sizes (*g*, *SE_g*) using the **Hedges-Olkin (HE)** τ² estimator and the **Knapp-Hartung** small-sample correction (`hakn = TRUE`). **Kostrzewa-Nowak et al. (2019)** is removed before pooling and the model re-fitted; `metafor::rma()` cross-validates.
:::

::: panel-tabset
### Full Model {meta}
```{r th2-main_meta_1}
m3 <- meta::metagen(TE = g, seTE = SE_g, data = fullData, studlab = paste(Study),
                    random = TRUE, method.tau = "HE", fixed = FALSE,
                    hakn = TRUE, prediction = TRUE, sm = "SMD")
print(m3, overall = TRUE)
```

### Full Model {metafor}
```{r th2-main-meta_2}
metafor::rma(yi = g, sei = SE_g, data = fullData, slab = paste(Study),
             method = "HE", test = "knha")
```

### Adapted Model {meta}
```{r th2-main-meta_3}
fullData <- drop_kostrzewa19(fullData)
m3 <- meta::metagen(g, seTE = SE_g, data = fullData, studlab = paste(Study),
                    random = TRUE, method.tau = "HE", hakn = TRUE,
                    prediction = TRUE, sm = "SMD", fixed = FALSE)
print(m3, overall = TRUE)
```
:::

## Outlier Detection

::: infobox
Leave-one-out standardised residuals are computed via `metaoutliers()`, which is passed the **variance** (`m3$seTE^2`). Studies with \|*z*\| \> 3 are flagged as outliers; \|*z*\| \> 1.96 warrants inspection.
:::

```{r th2-outliers}
outlier <- metaoutliers(y = m3$TE, s2 = m3$seTE^2, model = "RE")
stdres <- outlier$std.res
```

```{r}
#| label: tbl-th2-imm-resid
#| tbl-cap: "Standardised residuals"
fullData |> select(Short_reference, g) |> mutate(std_res = outlier$std.res) |> nice_table()
```

```{r th2-outliers-plot}
plot_stdres(stdres)
```

::: {.callout-caution}
One outcome has standardized residuals around -2 (Kostrzewa-Nowak et al. (2019)).
:::

## Funnel Plot & Influential Cases

::: infobox
The contour-enhanced funnel plot shows study estimates against their standard errors; shaded regions mark significance zones (α = 0.10, 0.05, 0.01). The dfbetas diagnostic from `metafor::rma.mv()` identifies **influential cases** — distinct from statistical outliers and not necessarily excluded.
:::

```{r th2-funnel}
#| fig-width: 10
#| fig-height: 8
#| out-width: 100%
funnel_ce(m3) #, ref = 0.3214, xlim = c(-1, 2), ylim = c(0.7, 0))
```

```{r}
#| label: tbl-th2-imm-dfbetas
#| tbl-cap: "DFBETAS influence diagnostics"
overall_metafor <- rma.mv(g, VE_g, tdist = TRUE, data = fullData)
df_betas <- dfbetas(overall_metafor)
fullData |> select(Short_reference, g) |> mutate(dfbetas = df_betas) |> nice_table()
```

::: {.callout-tip}
No influential case.
:::

## Forest Plot

```{r th2-forest}
#| fig-width: 8
#| fig-height: 7
#| out-width: 100%
forest_main(m3, xlim = c(-4, 3))
```

## Asymmetry Test

::: infobox
Egger's regression test (`method = "linreg"`) evaluates funnel asymmetry as a proxy for small-study/publication effects (one-tailed, *p* \< .10). Where asymmetry is suggested, a trim-and-fill analysis estimates potentially missing studies.
:::

```{r th2-egger}
metabias(m3, method = "linreg")
```

::: {.callout-note}
No asymmetry -> no trim-and-fill
:::

## Moderator Analyses

::: {.panel-tabset}

### Risk of Bias

::: infobox
Subgroup analysis by overall RoB rating tests whether study quality moderates the pooled effect; the between-subgroup statistic (*Q_b*) indicates whether subgroup means differ.
:::

#### Model
```{r th2-mod-rob}
m1mod <- update(m3, subgroup = RoB, print.subgroup.name = TRUE, fixed = FALSE)
print(m1mod, overall = FALSE)
```

::: {.callout-important}
Significant results
:::

#### Forrest Plot
```{r th2-mod-rob-forest}
#| fig-width: 10
#| fig-height: 12
#| out-width: 100%
forest_sub(m1mod, xlim = c(-4, 3))
```

#### Head-to-Head

::: infobox
**Head-to-head RoB comparisons.** Because the overall RoB subgroup test is significant, the individual rating levels are compared pairwise.
:::

::: {.panel-tabset}

##### Moderate vs Serious
```{r th2-mod-rob-h2h-mod-ser}
# Moderate vs Serious
fd_ms <- fullData |> dplyr::filter(!RoB == "Low") |> dplyr::filter(!RoB == "Critical")
m_ms  <- meta::metagen(g, VE_g, data = fd_ms, studlab = paste(Study), random = TRUE,
                       method.tau = "HE", hakn = TRUE, prediction = TRUE, sm = "SMD", fixed = FALSE)
print(update(m_ms, subgroup = RoB, print.subgroup.name = TRUE, fixed = FALSE), overall = FALSE)
```

::: {.callout-important}
Significant
:::

##### Moderate vs Low
```{r th2-mod-rob-h2h-mod-low}
# Moderate vs Low
fd_ml <- fullData |> dplyr::filter(!RoB == "Serious") |> dplyr::filter(!RoB == "Critical")
m_ml  <- meta::metagen(g, VE_g, data = fd_ml, studlab = paste(Study), random = TRUE,
                       method.tau = "HE", hakn = TRUE, prediction = TRUE, sm = "SMD", fixed = FALSE)
print(update(m_ml, subgroup = RoB, print.subgroup.name = TRUE, fixed = FALSE), overall = FALSE)
```

::: {.callout-important}
Significant
:::

##### Low vs Serious
```{r th2-mod-rob-h2h-low-ser}
# Low vs Serious
fd_ls <- fullData |> dplyr::filter(!RoB == "Critical") |> dplyr::filter(!RoB == "Moderate")
m_ls  <- meta::metagen(g, VE_g, data = fd_ls, studlab = paste(Study), random = TRUE,
                       method.tau = "HE", hakn = TRUE, prediction = TRUE, sm = "SMD", fixed = FALSE)
print(update(m_ls, subgroup = RoB, print.subgroup.name = TRUE, fixed = FALSE), overall = FALSE)
```

::: {.callout-note}
Not significant
:::

:::

### Sex

#### Model
```{r th2-mod-sex}
m2mod <- update(m3, subgroup = sex, print.subgroup.name = TRUE, fixed = FALSE)
print(m2mod, overall = FALSE)
```

::: {.callout-important}
Significant results but 15 vs 1 vs 2
:::

#### Forrest Plot
```{r th2-mod-sex-forest}
#| fig-width: 10
#| fig-height: 8
#| out-width: 100%
forest_sub(m2mod, xlim = c(-4, 3))
```

### Intensity

#### Model
```{r th2-mod-intensity}
fullData_bis <- fullData |> dplyr::filter(!intensity == "")
m1_c <- meta::metagen(g, seTE = SE_g, data = fullData_bis, studlab = paste(Study),
                      random = TRUE, method.tau = "HE", hakn = TRUE,
                      prediction = TRUE, sm = "SMD", fixed = FALSE)
m3mod <- update(m1_c, subgroup = intensity, print.subgroup.name = TRUE, fixed = FALSE)
print(m3mod, overall = FALSE)
```

::: {.callout-note}
Not significant
:::

#### Forrest Plot
```{r th2-mod-intensity-forest}
#| fig-width: 10
#| fig-height: 8
#| out-width: 100%
forest_sub(m3mod, xlim = c(-4, 3))
```

### Staining

```{r th2-mod-staining}
m4mod <- update(m3, subgroup = staining, print.subgroup.name = TRUE, fixed = FALSE)
print(m4mod, overall = FALSE)
```

::: {.callout-important}
Significant results
:::

### Continuous Moderators (Meta-Regression)

::: infobox
Continuous moderators are tested via weighted meta-regression (`metareg()`). A significant slope indicates the moderator explains part of the between-study heterogeneity (τ²); bubble plots show the fitted line with 95% CI.
:::

::: {.panel-tabset}

#### Age
```{r th2-mr-age}
m1mr <- metareg(m3, age); summary(m1mr)
```

::: {.callout-important}
Significant
:::

```{r th2-mr-age-bubble}
#| fig-width: 10
#| fig-height: 8
#| out-width: 100%
bubble_reg(m1mr, "age", "Age (years)")
```

#### BMI
```{r th2-mr-bmi}
m2mr <- metareg(m3, bmi); summary(m2mr)
```

::: {.callout-note}
Not significant
:::

```{r th2-mr-bmi-bubble}
#| fig-width: 10
#| fig-height: 8
#| out-width: 100%
bubble_reg(m2mr, "bmi", "BMI (kg/m²)")
```

#### Duration
```{r th2-mr-duration}
m3mr <- metareg(m3, duration); summary(m3mr)
```

::: {.callout-note}
Not significant
:::

#### Dose
```{r th2-mr-dose}
m4mr <- metareg(m3, dose); summary(m4mr)
```

::: {.callout-note}
Not significant
:::

#### IFN
```{r th2-mr-ifn}
m6mr <- metareg(m3, IFN); summary(m6mr)
```

::: {.callout-note}
Not significant
:::

#### IL_4
```{r th2-mr-il4}
m7mr <- metareg(m3, IL_4); summary(m7mr)
```

::: {.callout-note}
Not significant
:::

#### IL_6
```{r th2-mr-il6}
m8mr <- metareg(m3, IL_6); summary(m8mr)
```

::: {.callout-note}
Not significant
:::

#### IL_10
```{r th2-mr-il10}
m9mr <- metareg(m3, IL_10); summary(m9mr)
```

::: {.callout-note}
Not significant
:::

#### IL_2
```{r th2-mr-il2}
m10mr <- metareg(m3, IL_2); summary(m10mr)
```

::: {.callout-note}
Not significant
:::

:::

:::

## Multivariate Models

::: {.panel-tabset}

### Intensity * Duration
```{r th2-multivariate-int-dur}
rma(yi = g, vi = V_g, mods = ~ intensity * duration, data = fullData,
    slab = paste(Study), method = "HE", test = "knha")
```

::: {.callout-note}
Not significant
:::

### IL_10 * IL_4
```{r th2-multivariate-il_10-4}
rma(yi = g, vi = V_g, mods = ~ IL_10 * IL_4, data = fullData,
    slab = paste(Study), method = "HE", test = "knha")
```

::: {.callout-note}
Not significant
:::

:::
