# T~H~2 - 2 h post-exercise

```{r}
#| include: false
for (p in c("R/_common.R", "../R/_common.R", "book/R/_common.R")) if (file.exists(p)) { source(p); break }
source(file.path(dirname(p), "_chapter_helpers.R"))
knitr::opts_knit$set(root.dir = normalizePath(dirname(dirname(p))))
knitr::opts_chunk$set(echo = FALSE)
cfg <- list(
  id = "th2-2h",
  outcome = "Th2",
  win = "pre_post+2h",
  M = "m3",
  drop_kost = FALSE,
  tabs = c("M0-meta", "M0-metafor"),
  forest = list(w = 8, h = 4, args = "left = \"Lower at post+2h\", right = \"Higher at post+2h\""),
  asym = "none",
  lancaster = TRUE
)
chain <- chapter_chain(cfg)
```

::: {.summary-panel}
[Summary]{.panel-eyebrow}

## Sensitivity Overview

`r badge(reported_id(cfg), MODEL_LABEL[[reported_id(cfg)]], chain[[R_MAIN]][[reported_id(cfg)]]$k)`

```{r}
sens_overview_table(cfg, chain)
```

```{r}
#| fig-height: 2.4
#| out-width: 100%
sens_overview_plot(cfg, chain)
```

## Model Ledger

```{r}
ledger_table(cfg, chain)
```
:::

[Analysis]{.panel-eyebrow .analysis-eyebrow}

```{r}
r_switch(cfg)
```

```{r}
chapter_resources(cfg, chain)
```

## Data Import

::: infobox
The ~2 h window (`effect_size/Th2/pre_post+2h/Th2_pre_post+2h_r_050.csv`) is reported for the main analysis, outlier check, funnel, and forest only; the limited data do not support moderator modelling. No study is excluded a priori.
:::

```{r}
#| results: asis
sec(sec_data)
```

## Primary Meta-Analysis

```{r}
#| results: asis
sec(sec_primary)
```

## Outlier Detection

```{r}
#| results: asis
sec(sec_outlier)
```

::: {.callout-note}
One outcome has standardized residuals around -2 (Kostrzewa-Nowak et al. (2019)).
:::

[r = .50]{.callout-r}

## Funnel Plot & Influential Cases

```{r}
#| results: asis
sec(sec_funnel)
```

::: {.callout-note}
No influential case.
:::

[r = .50]{.callout-r}

## Forest Plot

```{r}
#| results: asis
sec(sec_forest)
```

## Asymmetry Test

::: warnbox
**Note:** the number of studies in this window is too small to reliably test for small-study effects (minimum *k* = 10). No Egger's test or trim-and-fill is performed.
:::

## Sensitivity Analyses

```{r}
#| results: asis
sec(sec_lancaster)
```
