# Workspace Setup

```{r}
#| include: false
for (p in c("R/_common.R", "../R/_common.R", "book/R/_common.R")) if (file.exists(p)) { source(p); break }
source(file.path(dirname(p), "_chapter_helpers.R"))
knitr::opts_knit$set(root.dir = normalizePath(dirname(dirname(p))))
```

```{r}
#| echo: false
page_resources(list(
  c("GitHub repository", REPO_URL, "github"),
  c("Meta-analysis R script", "../R/meta_Th1Th2.R", "file-earmark-code"),
  c("Shared setup (_common.R)", "../R/_common.R", "file-earmark-code"),
  c("Chapter helpers (_chapter_helpers.R)", "../R/_chapter_helpers.R", "file-earmark-code")
))
```

::: infobox
All chapters load a shared setup file (`_common.R`) that installs/loads the required packages, sets a consistent global `ggplot2` theme, defines the leave-one-out outlier-detection functions, and exposes small helpers for the standard funnel, forest, and bubble plots used throughout. This keeps every analysis chapter self-contained and reproducible regardless of render order.
:::

## Packages

```{r}
#| echo: false
pkg_groups <- list(
  "Meta-analysis"   = c("meta", "metafor", "metaviz", "forestplot"),
  "Data handling"   = c("dplyr", "tidyr", "data.table", "stringr", "readr", "readxl", "reshape2"),
  "Visualisation"   = c("ggplot2", "plotly", "patchwork", "cowplot", "gridExtra", "scales"),
  "Tables & export" = c("kableExtra", "writexl", "zip")
)
card <- function(p) {
  d <- utils::packageDescription(p)
  sprintf('<a class="pkg-card" href="https://CRAN.R-project.org/package=%s" target="_blank" rel="noopener"><span class="pkg-name">%s</span><span class="pkg-ver">%s</span><span class="pkg-title">%s</span></a>',
          p, p, d$Version, gsub("[\n ]+", " ", gsub("'", "", d$Title)))
}
html <- paste0(vapply(names(pkg_groups), function(g) sprintf(
  '<div class="pkg-group"><div class="panel-eyebrow">%s</div><div class="pkg-grid">%s</div></div>',
  g, paste(vapply(pkg_groups[[g]], card, character(1)), collapse = "")), character(1)), collapse = "")
knitr::asis_output(paste0("\n```{=html}\n<div class=\"pkg-wrap\">", html,
  sprintf('<div class="pkg-meta">%s</div>', R.version.string), "</div>\n```\n"))
```

<details class="raw-output"><summary>Installation code</summary>

```{r show-packages}
#| eval: false
#| code-fold: false
requiredlibraries <- c(
  "metafor", "tidyr", "dplyr", "data.table", "stringr", "readr",
  "ggplot2", "reshape2", "cowplot", "gridExtra",
  "forestplot", "metaviz", "meta",
  "readxl", "patchwork", "scales", "kableExtra",
  "plotly", "writexl", "zip"
)

# Install any that are missing, then load all of them.
missing_packages <- requiredlibraries[
  !sapply(requiredlibraries, requireNamespace, quietly = TRUE)
]
if (length(missing_packages) > 0) install.packages(missing_packages, dependencies = TRUE)
invisible(lapply(requiredlibraries, library, character.only = TRUE))
```

</details>

## Outlier and Influence Diagnostics

::: infobox
**Custom functions - required for all outlier analyses below.**

The following four functions implement the leave-one-out standardised residual approach described in @hedgesDiagnosticProceduresResearch1985 and @viechtbauerOutlierInfluenceDiagnostics2010. A study is classified as an outlier if its standardised residual exceeds \|3\|; values above \|1.96\| warrant closer inspection. The model (fixed- vs. random-effects) is selected automatically from the robust heterogeneity index *I*r² (\< 30% → fixed-effects, otherwise random-effects). The outlier routine is always passed the **variance** (`seTE^2`) as its `s2` argument.
:::

### Decision procedure

```{mermaid}
%%| echo: false
%%| fig-width: 6.5
flowchart TD
  A["M1 - Primary<br/>random-effects model"] --> B["Leave-one-out standardised residuals<br/><code>metaoutliers(y, s2 = seTE^2)</code>"]
  B --> C{"|z| ≥ 3"}
  C -- no --> D["|z| > 1.96: inspect<br/>otherwise: no outlier"]
  C -- yes --> E["Outlier"]
  A --> F["DFBETAS<br/><code>rma.mv()</code>"]
  F --> G{"|DFBETAS| > 1"}
  G -- yes --> H["Influential case"]
  G -- no --> I["Not influential"]
  E --> J{"Outlier and<br/>influential?"}
  H --> J
  J -- yes --> K["Withdraw and re-fit<br/>M2 - Outlier-adjusted"]
  J -- no --> L["Retain all outcomes<br/>heterogeneity: moderator analyses"]
  D --> L
  I --> L
  classDef model fill:#F0F6FF,stroke:#0078D4,color:#1E1E1E
  classDef flag fill:#FDECEC,stroke:#C62828,color:#8B1A1A
  classDef keep fill:#F7F7F7,stroke:#9AA0A6,color:#1E1E1E
  class A,K model
  class E,H flag
  class D,I,L keep
```

### Example

```{r}
#| include: false
ex_cfg <- list(outcome = "Th1", win = "pre_post17h", drop_kost = TRUE)
ex_dat <- drop_kostrzewa19(load_es(es_file(ex_cfg, R_MAIN)))
ex_m   <- .fit(ex_dat)
ex_out <- metaoutliers(y = ex_m$TE, s2 = ex_m$seTE^2, model = "RE")
ex_dfb <- dfbetas(rma.mv(g, VE_g, tdist = TRUE, data = ex_dat))[[1]]
```

`r badge("M1", "Primary", ex_m$k)` [T~H1~ - 17 h post-exercise - r = .50]{.panel-eyebrow .eyebrow-plain}

::: panel-tabset
### Standardised residuals

```{r}
#| echo: false
#| fig-height: 5
#| out-width: 100%
plot_stdres(ex_out$std.res, labels = ex_dat$Short_reference)
```

### DFBETAS

```{r}
#| echo: false
#| fig-height: 5
#| out-width: 100%
plot_dfbetas(ex_dfb, labels = ex_dat$Short_reference)
```
:::

### Functions

```{r show-outlier-functions}
#| eval: false
metaoutliers  <- function(y, s2, model) { ... }   # leave-one-out standardised residuals
metahet.base  <- function(y, s2)        { ... }   # heterogeneity measures (Q, I², τ², robust Ir²)
tau2.r.solver <- function(w, Qr)        { ... }   # robust τ² (mean-based)
tau2.m.solver <- function(w, Qm)        { ... }   # robust τ² (median-based)
```

The full definitions live in `_common.R` and are sourced automatically at the top of every chapter.
